Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-04 General WLD combinatorics.tex

% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

% Also talk about Le diagrams.

[We probably need a subsection for background here. Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will. ]

@@

Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
\[J_p^{(W)}(i) = \{m \in [n] \ : \ I^{(W)}_m(p) = i \},\]
i.e. the set of indices $m$ for which Algorithm [ref] assigns the value $i$ to the propagator $p$ in $W$. The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.

@@

Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.  Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices play no role in Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

\begin{figure}
    \includegraphics[scale=0.8]{3cases}
    \caption{Four cases for admissible WLDs with no non-supporting vertices. The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
  \end{figure}

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (although this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary). Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).

\begin{figure}
\includegraphics[scale=0.8]{Vdiagram_modified}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{(V)} = J_r^{(W)}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.  Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$. The result therefore holds in this case.

Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
We first describe $J_q^{(V)}(*)$, which can be handled identically for all three cases.

In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
\[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$. Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
\[J^{(V)}_q(i) = [j+2,d-1], \quad J^{(V)}_q(i+1) = [d,e-1], \quad J^{(V)}_q(j) = [e,j], \quad J^{(V)}_q(j+1) = \{j+1\},\]
and all intervals are non-empty.

We now consider what happens as we move from $V$ to each of the three remaining cases for $W$. We need to consider both $J^{(W)}_p$ and $J^{(W)}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.

@@

\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously. Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.  Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.  Note that $l, \ldots, l+a-1$ are all in the support of $p$.

We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{(W)}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e. on the value of $I^{(V)}_w(q)$. Thus, if $w\in J_q^{(V)}(i)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{(W)}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{(W)}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{(V)}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{(W)}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.  $X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.  Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.  Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.  Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$. Therefore
       \[
       I_j^{(W)}(r) = \begin{cases}

       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
       I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
       \] 
Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{(W)}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]
Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$. We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.  However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.  In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.

Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
    \[
    I_{j+1}^{(W)}(r)  = \begin{cases}
      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
    \end{cases}
    \]
We can now describe the intervals $J^{(W)}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}. For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \begin{gather*}
    J^{(W)}_p(m) = [m+4, m], \qquad  J^{(W)}_p(m+1) = \{m+1\}, \\ J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
    \end{gather*}
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \begin{gather*}
    J^{(W)}_p(m) = [m+4, d-1], \qquad  J^{(W)}_p(m+1) = [d, m+1], \\  J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
    \end{gather*}
    which are nonempty and otherwise as required.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \begin{gather*}
    J^{(W)}_p(m) = \{m+4\}, \qquad  J^{(W)}_p(m+1) = [m+5, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
    \end{gather*}
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \begin{gather*}
    J^{(W)}_p(m) = [m+4, j+1], \qquad  J^{(W)}_p(m+1) = [j+2, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
    \end{gather*}
    which are again as required.
    \end{itemize}

\textbf{Third case}: In this case there are no unsupported vertices $l, l+1, \ldots$ inside $q$.  Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$. We proceed as in the previous cases, by computing $I^{(W)}_w$ for vertices $w$ in roughly increasing order of difficulty.

For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]

@@

\begin{align*}
  I_{j+1}^{(W)}(r) &= \begin{cases}
    j+1 & \text{if } r=q\\
    j+2 & \text{if } r=p\\
    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_m^{(W)}(r) &= \begin{cases}
    m & \text{if $r=p$ and $q$ not supported on $m$}\\
    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
    I_{m}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+1}^{(W)}(r) & = \begin{cases}
    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_{m+2}^{(W)}(r) & = \begin{cases}
    m+2 & \text{if } r=p \\
    I_{m+3}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+3}^{(W)}(r) & = \begin{cases}
    m+3 & \text{if } r=p \\
    I_{m+4}^{(V)}(r) & \text{if } r\neq p
  \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.

Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
\begin{itemize}
\item if $m=j$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+1$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+2$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
\end{itemize}
The result now follows by induction.
\end{proof}

>>>>

Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

Also talk about Le diagrams.

@@

Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$ we will use the notation $J_p^{(W)}(i)$ for the set of indices $m$ where $I_m(p) = l$ where the $I_m$ are the sets calculated by Algorithm~\ref{alg:put GN on WLD}, and using the notation of Definition~\ref{def I_i as a function}.

@@

Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.  Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
\end{lem}

\begin{proof}

We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices play no role in Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

  \begin{figure}
    \includegraphics[scale=0.8]{3cases}
    \caption{Four cases for admissible WLDs with no unsupported vertices. The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
  \end{figure}

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q = (i,j)$ with no other propagators inside it (although this region may or may not contain unsupported vertices which we will call $l, l+1, \ldots$ as necessary). Call this diagram $V$ (figure \ref{fig V diagram}).

\begin{figure}
\includegraphics[scale=0.8]{Vdiagram_modified}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.  Additionally, $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.

Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
We first describe $J_q^{(V)}(*)$: since there are no propagators inside $q$, we see from the diagram that
\[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis. Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
\[J^{(V)}_q(i) = [j+2,d-1], \quad J^{(V)}_q(i+1) = [d,e-1], \quad J^{(V)}_q(j) = [e,j], \quad J^{(V)}_q(j+1) = \{j+1\},\]
and all intervals are non-empty.

We now examine what happens in each of the three cases.

@@

\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.  Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.  Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.  Note that $l, \ldots, l+a-1$ are all in the support of $p$.  We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
      \]
For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.  Thus in both cases, we have for any $0\leq b <a$
    \[
    I_{l+b}^{(W)}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b}^{(V)}(r) & \text{if } r\neq p
    \end{cases}
    \]
    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
     \[
       I_j^{(W)}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
       \end{cases}
       \]
       If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.  In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.  Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.  $X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.  Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.  Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.  Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.  Therefore
       \[
       I_j^{(W)}(p) = m \text{ if $j$ is not in the support of $p$}
       \]

For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{(W)}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]
%Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
%       ***these intervals need checking***
%\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
%  where
%  \[
%  c = \begin{cases} d-1 & \text{if } m=i+1 \\
%    j-2 & \text{otherwise}
%      \end{cases}
%  \]
%also satisfies the statement of the theorem.

Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$. We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.  However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.  In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$. 
    Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
    \[
    I_{j+1}^{(W)}(r)  = \begin{cases}
      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
    \end{cases}
    \]

    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \[
    J^{(W)}_p(m) = [m+4, m], \  J^{(W)}_p(m+1) = \{m+1\}, \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \[
    J^{(W)}_p(m) = [m+4, d-1], \  J^{(W)}_p(m+1) = [d, m+1], \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \[
    J^{(W)}_p(m) = \{m+4\}, \  J^{(W)}_p(m+1) = [m+5, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \[
    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are again as required.
    \end{itemize}

\textbf{Third case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.  Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$. For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]

@@

\begin{align*}
  I_{j+1}^{(W)}(r) &= \begin{cases}
    j+1 & \text{if } r=q\\
    j+2 & \text{if } r=p\\
    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_m^{(W)}(r) &= \begin{cases}
    m & \text{if $r=p$ and $q$ not supported on $m$}\\
    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
    I_{m}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+1}^{(W)}(r) & = \begin{cases}
    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_{m+2}^{(W)}(r) & = \begin{cases}
    m+2 & \text{if } r=p \\
    I_{m+3}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+3}^{(W)}(r) & = \begin{cases}
    m+3 & \text{if } r=p \\
    I_{m+4}^{(V)}(r) & \text{if } r\neq p
  \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$. Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.  Assembling the intervals for $p$ we get,
 if $m=j$ then
\[J_p^{(W)}(m) = [m+4,e-1], \  J_p^{(W)}(m+1) = [e,m], \  J_p^{(W)}(m+2) = [m+1,m+2], \  J_p^{(W)}(m+3) = \{m+3\},\]
 if $m=j+1$ then
\[J_p^{(W)}(m) = [m+4,m-1], \ J_p^{(W)}(m+1) = [m,m+1], \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\},\]
and if $m=j+2$ then
\[J_p^{(W)}(m) = [m+4,m], \  J_p^{(W)}(m+1) = \{m+1\}, \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\}.\]
The result now follows by induction.
\end{proof}
